---
title: "Twin Valkyrs"
output: html_document
date: "2023-09-12"
---

## Settings 

### -Libraries

```{r}
knitr::opts_chunk$set(echo = TRUE)
source("./scripts/0_0_Libraries.R")
```

### -Utils

```{r}
source(file = "./scripts/0_1_DownloadUtils.R")
```

### -Auth Token request

```{r}
## Run once
# token <- POST("https://www.warcraftlogs.com/oauth/token",
#           config = list(),
#           body = list(
#             grant_type="client_credentials",
#             client_id=Sys.getenv("client_id"),
#             client_secret=Sys.getenv("client_secret")))
# 
# token <- content(token,"parsed")
# 
# Manually copy token to .env file and load locally
```

```{r}
token <- Sys.getenv("TOKEN")

url <- "https://classic.warcraftlogs.com/api/v2"

WCL_API2_request <- function(request) {
  
  tryCatch({
    
    request <- jsonlite::toJSON(list(query=request),
                                auto_unbox=TRUE,
                                bigint_as_char=F)
    
    
    response <- POST(url,
                     add_headers("Content-Type" = "application/json",
                                 "Authorization"= paste0("Bearer ",
                                                         token)),
                     body = request,
                     content_type_json(),
                     encode = "json")
    
    response_formated <- fromJSON(content(response,
                                          as = "text",
                                          encoding="UTF-8"),
                                  bigint_as_char=TRUE)
    
    return(response_formated)
  }, error = function(e) {
    # Handle the error here or return an informative message
    cat("Error in WCL_API2_request:", e$message, " Request: ",request,"\n")
    return(NULL)  # Return an appropriate value or error indicator
  })
}

```

## Download random log data

```{r}
source(file = "./scripts/1_0_logID_download.R")
```

### - Merge

```{r}
df1 <- read.csv("raw_data/past_logs/response_logs_code_df_TwinRAW_2023_09_21_h03_m57.csv")
df2 <- read.csv("raw_data/past_logs/response_logs_code_df_TwinsRAW_2023_09_20_h03_m50.csv")
df3 <- read.csv("raw_data/past_logs/response_logs_code_df2023_08_29.csv")
df4 <- read.csv("raw_data/past_logs/response_logs_code_df_2023_09_22.csv")


df <- bind_rows(df1,df2,df3,df4) %>%
  distinct(code, .keep_all = TRUE) %>%
  mutate(LogstartTime = as_datetime(as.POSIXct(startTime/1000, origin="1970-01-01")),
         LogendTime = as_datetime(as.POSIXct(endTime/1000, origin="1970-01-01")),
         logNote ="Random Logs") %>%
  select(-c(X)) %>% rename(logID = code)
```

### - Encounter data

```{r}
logIDs <- unique(df$logID)

request_encounter <- sprintf(request_encounter_str, logIDs)

response_formatted_list <- lapply(seq_along(request_encounter), function(i) {  
  
  response <- WCL_API2_request(request_encounter[i])$data$reportData$report$fights 
  
  if (i %% 25 == 0) {
    cat("Processed", i, "out of", length(request_encounter), "\n")
  }
  
  if(!is.null(response) & length(response)>0) {
    
    response <- mutate(response, 
                       duration = endTime - startTime,  
                       duration_s = duration/1000,
                       logID = as.character(logIDs[i]),
                       logStart = as.character(df$LogstartTime[i]),
                       logEnd = as.character(df$LogendTime[i]),
                       logNote = as.character(df$logNote[i])
    )
    
    response <- rename(response,fightID = id)
    
  } else {
    response <- data.frame(logID = as.character(df$logID[i]),
                           logStart = as.character(df$LogstartTime[i]),
                           logNote = as.character(df$logNote[i]),
                           fightID=0,
                           encounterID=0
                           
    )
  }
  return(response)
})

encounter_response_list<- response_formatted_list
rm(response_formatted_list)
encounter_data <- do.call(bind_rows, encounter_response_list)

write.csv(encounter_data,paste0("encounter_data",format(Sys.time(), "%Y_%m_%d_h%H_m%M"),".csv"))
```


## Download top log data

```{r}
source(file = "./scripts/1_1_rankings_download.R")
```

### - Merge

```{r}
df1 <- read.csv("raw_data/df_rankings_execution_2023_09_23_h14_m28.csv")
df2 <- read.csv("raw_data/df_rankings_progress_2023_09_23_h14_m27.csv")
df3 <- read.csv("raw_data/df_rankings_speed_2023_09_23_h14_m26.csv")

df <- bind_rows(df1,df2,df3) %>%
  distinct(report.code, .keep_all = TRUE) %>%
  mutate(LogstartTime = as_datetime(as.POSIXct(report.startTime/1000, origin="1970-01-01")),
         logNote ="Top Logs") %>%
  select(-c(X)) %>% rename(logID = report.code)
```

### - Encounter data

```{r}
logIDs <- unique(df$logID)

request_encounter <- sprintf(request_encounter_str, logIDs)

output <- lapply(seq_along(request_encounter), function(i) {  
  
  response <- WCL_API2_request(request_encounter[i])$data$reportData$report$fights 
  
  if (i %% 25 == 0) {
    cat("Processed", i, "out of", length(request_encounter), "\n")
  }
  
  if(!is.null(response) & length(response)>0) {
    
    response <- mutate(response, 
                       duration = endTime - startTime,  
                       duration_s = duration/1000,
                       logID = as.character(logIDs[i]),
                       logStart = as.character(df$LogstartTime[i]),
                       logNote = as.character(df$logNote[i])
    )
    
    response <- rename(response,fightID = id)
    
  } else {
    response <- data.frame(logID = as.character(df$logID[i]),
                           logStart = as.character(df$LogstartTime[i]),
                           logNote = as.character(df$logNote[i]),
                           fightID=0,
                           encounterID=0
                           
    )
  }
  return(response)
})

encounter_data_topLogs <- do.call(bind_rows, output)

write.csv(encounter_data_topLogs,paste0("encounter_data_topLogs_",format(Sys.time(), "%Y_%m_%d_h%H_m%M"),".csv"))
```


## Process both logs

```{r}
encounter_data <- read.csv("encounter_data2023_09_22.csv")

#encounter_data %>% filter(encounterID!=0) %>% group_by(logID) %>% summarise(n=n()) %>% nrow(.)

twins_df <- ## 13,567
encounter_data %>% filter(encounterID!=0) %>% 
  filter(encounterID==641 & duration_s>=50) 

#twins_df %>% group_by(logID) %>% summarise(n=n()) %>% nrow(.)


twins_df <- twins_df%>%
  
  mutate(duration_s_filter = round(duration_s,1),
         logdate = as.Date(logStart))%>%
  
  distinct(difficulty, size, kill, fightPercentage, 
           duration_s_filter, averageItemLevel,logdate,
           .keep_all = TRUE) ## 10,420

#twins_df %>% group_by(logID) %>% summarise(n=n()) %>% nrow(.)

twins_df %>% group_by(size) %>% summarise(n=n())
twins_df %>% filter(size==10) %>% group_by(logID) %>% summarise(n=n()) %>% nrow(.)
twins_df %>% filter(size==25) %>% group_by(logID) %>% summarise(n=n()) %>% nrow(.)

twins_df %>% group_by(size,difficulty) %>% summarise(n=n())
twins_df %>% filter(size==25 & difficulty==3) %>% group_by(logID) %>% summarise(n=n()) %>% nrow(.)
twins_df %>% filter(size==25 & difficulty==4) %>% group_by(logID) %>% summarise(n=n()) %>% nrow(.)
twins_df %>% filter(size==10 & difficulty==3) %>% group_by(logID) %>% summarise(n=n()) %>% nrow(.)
twins_df %>% filter(size==10 & difficulty==4) %>% group_by(logID) %>% summarise(n=n()) %>% nrow(.)


encounter_data_top <- read.csv("encounter_data_topLogs_2023_09_24.csv")

#encounter_data %>% filter(encounterID!=0) %>% group_by(logID) %>% summarise(n=n()) %>% nrow(.)

twins_df_top <- ## 13,567
encounter_data_top %>% filter(encounterID!=0) %>% 
  filter(encounterID==641 & duration_s>=50) 

#twins_df %>% group_by(logID) %>% summarise(n=n()) %>% nrow(.)


twins_df_top <- twins_df_top%>%
  
  mutate(duration_s_filter = round(duration_s,1),
         logdate = as.Date(logStart))%>%
  
  distinct(difficulty, size, kill, fightPercentage, 
           duration_s_filter, averageItemLevel,logdate,
           .keep_all = TRUE) ## 10,420

```

## Download Essence and Ability

```{r}
#65874 - Shield of Darkness
#65858- Shield of Lights

#66058 - Dark Vortex 
#66046 - Light Vortex

#65684 - Dark Essence
#65686 - Light Essece
TWinEssence <-"ability.id in (65684,65686) or type = 'combatantinfo'"


TwinAblity <-"ability.id in (65874,65858,66058,66046)"
```


```{r}
twins_df <- bind_rows(twins_df_top,twins_df)
```

### - Essence

```{r}
df_select <- twins_df  %>%
  select(logID,fightID) 

#### -balancection Initial specs
request_logs_code <- sprintf(request_twins_essence_str,
                             df_select$logID,
                             df_select$fightID,
                             TWinEssence)

request_logs_code <- request_logs_code

n_total <- length(request_logs_code)

output <- lapply(seq_along(request_logs_code), function(i) {  
  
  
  response <- WCL_API2_request(request_logs_code[i]
  )$data$reportData$report$events$data
  
  if (!is.null(response) & length(response)>0) {
    response <- response %>%
      mutate(logID =  as.character(twins_df$logID[i]),
             fightID = as.integer(twins_df$fightID[i]),
             size = as.integer(twins_df$size[i]),
             difficulty = as.integer(twins_df$difficulty[i]),
             kill = as.integer(twins_df$kill[i]),
             startTime = as.integer(twins_df$startTime[i]),
             duration_s = as.integer(twins_df$duration_s[i]),
             logNote = as.character(twins_df$logNote[i]),
             averageItemLevel = as.character(twins_df$averageItemLevel[i]),
             fightPercentage = as.character(twins_df$fightPercentage[i])
             
      )
  } else {
    response <- data.frame(timestamp=-1,
                           logID = as.character(twins_df$logID[i]),
                           fightID = as.integer(twins_df$fightID[i]),
                           size = as.integer(twins_df$size[i]),
                           difficulty = as.integer(twins_df$size[i]),
                           kill = as.integer(twins_df$kill[i]),
                           startTime = as.integer(twins_df$startTime[i]),
                           duration_s = as.integer(twins_df$duration_s[i]),
                           logNote = as.character(twins_df$logNote[i]),
                           averageItemLevel = as.character(twins_df$averageItemLevel[i]),
                           fightPercentage = as.character(twins_df$fightPercentage[i])
    )
  }
  
  if (i %% 100 == 0) {
    cat("Processed encounter",i, "out of", n_total,"Twin Valkyr Encounters\n")
  }
  
  return(response)
})

output2 <- do.call(bind_rows, output)


output3<- output2 %>%
  filter(type != "combatantinfo") %>%
  
  select(timestamp,logID,fight,fightID,type,sourceID,targetID,abilityGameID,
         #hitPoints,maxHitPoints,
         #x,y,
         size,difficulty,kill,startTime,duration_s,averageItemLevel,fightPercentage,logNote) 



write.csv(output3,paste0("./output_twinsvalkyr_essence_",format(Sys.time(), "%Y_%m_%d_h%H_m%M"),".csv"))
saveRDS(output2, paste0("./output_full_twinsvalkyr_essence_",format(Sys.time(), "%Y_%m_%d_h%H_m%M"),".rds"))


#output2_test <- readRDS("./output_full_twinsvalkyr_2023_09_23_h07_m21.rds")

```

### - Ability

```{r}
df_select <- twins_df  %>%
  select(logID,fightID) 

#### -balancection Initial specs
request_logs_code <- sprintf(request_twins_cast_str,
                             df_select$logID,
                             df_select$fightID,
                             TwinAblity)

request_logs_code <- request_logs_code

n_total <- length(request_logs_code)

output <- lapply(seq_along(request_logs_code), function(i) {  
  
  
  response <- WCL_API2_request(request_logs_code[i]
  )$data$reportData$report$events$data
  
  if (!is.null(response) & length(response)>0) {
    response <- response %>%
      mutate(logID =  as.character(twins_df$logID[i]),
             fightID = as.integer(twins_df$fightID[i]),
             size = as.integer(twins_df$size[i]),
             difficulty = as.integer(twins_df$difficulty[i]),
             kill = as.integer(twins_df$kill[i]),
             startTime = as.integer(twins_df$startTime[i]),
             duration_s = as.integer(twins_df$duration_s[i]),
             logNote = as.character(twins_df$logNote[i]),
             averageItemLevel = as.character(twins_df$averageItemLevel[i]),
             fightPercentage = as.character(twins_df$fightPercentage[i])
             
      )
  } else {
    response <- data.frame(timestamp=-1,
                           logID = as.character(twins_df$logID[i]),
                           fightID = as.integer(twins_df$fightID[i]),
                           size = as.integer(twins_df$size[i]),
                           difficulty = as.integer(twins_df$size[i]),
                           kill = as.integer(twins_df$kill[i]),
                           startTime = as.integer(twins_df$startTime[i]),
                           duration_s = as.integer(twins_df$duration_s[i]),
                           logNote = as.character(twins_df$logNote[i]),
                           averageItemLevel = as.character(twins_df$averageItemLevel[i]),
                           fightPercentage = as.character(twins_df$fightPercentage[i])
    )
  }
  
  if (i %% 100 == 0) {
    cat("Processed encounter",i, "out of", n_total,"Twin Valkyr Encounters\n")
  }
  
  return(response)
})

output2 <- do.call(bind_rows, output)


output3<- output2 %>%
  filter(type != "combatantinfo") %>%
  
  select(timestamp,logID,fight,fightID,type,sourceID,targetID,abilityGameID,
         #hitPoints,maxHitPoints,
         #x,y,
         size,difficulty,kill,startTime,duration_s,averageItemLevel,fightPercentage,logNote) 



write.csv(output3,paste0("./output_twinsvalkyr_essence_",format(Sys.time(), "%Y_%m_%d_h%H_m%M"),".csv"))
saveRDS(output2, paste0("./output_full_twinsvalkyr_essence_",format(Sys.time(), "%Y_%m_%d_h%H_m%M"),".rds"))


#output2_test <- readRDS("./output_full_twinsvalkyr_2023_09_23_h07_m21.rds")

```


## Process all data

### - Load

```{r}
df_special <- read.csv("output_twinsvalkyr_2023_09_24_h23_m13.csv") %>% 
  select(-c(X))

dfexe <- read.csv("./raw_data/top_logs/df_rankings_execution_2023_09_23_h14_m28.csv")
dfprog <- read.csv("./raw_data/top_logs/df_rankings_progress_2023_09_23_h14_m27.csv")
dfspeed <- read.csv("./raw_data/top_logs/df_rankings_speed_2023_09_23_h14_m26.csv")


essence <- read.csv("output_twinsvalkyr_essence_2023_09_25_h09_m37.csv") %>% 
  select(-c(X,logNote)) %>%
  distinct(across(everything())) #5012072

```

### - Essence data

```{r}

df_essence <- essence %>%
  group_by(logID,fightID,abilityGameID) %>%
  summarise(n=n()) %>%

  ungroup() %>%

  pivot_wider(names_from = abilityGameID,
              values_from = n) %>%

  clean_names() %>% rename("Dark"=x65684,
                           "Light"=x65686)%>%
  filter(!is.na(log_id)) %>%
  filter(!is.na(fight_id)) %>%
  mutate_if(is.integer, ~coalesce(., 0)) %>%

  mutate(Raid_Color = ifelse(Dark/Light<=2  & Dark/Light>=0.5,"Uncertain",
                             ifelse(Dark>Light &  Dark/Light>=2,"Dark","Light")))


write.csv(df_essence,"./raw_data/RAW_twinsvalkyr_public_essenceonly.csv")
```

### - Region data

```{r}
region <- dfspeed %>% select(logID=report.code,
                             fightID = report.fightID,
                             server.region)
```

### - Ranking data

```{r}
dfexe <- dfexe %>% select(logID = report.code,
                          fightID = report.fightID) %>%
  mutate(Exe = "Execution")%>%
  filter(!is.na(logID))%>%
  filter(!is.na(fightID))

dfprog <- dfprog %>% select(logID = report.code,
                          fightID = report.fightID) %>%
  mutate(Prog = "Progression")%>%
  filter(!is.na(logID))%>%
  filter(!is.na(fightID))

dfspeed <- dfspeed %>% select(logID = report.code,
                          fightID = report.fightID) %>%
  mutate(Speed = "Speed")%>%
  filter(!is.na(logID))%>%
  filter(!is.na(fightID))
```


```{r}
abcde <- full_join(dfexe,dfprog,by=c("logID","fightID")) %>%
  full_join(dfspeed,by=c("logID","fightID"))


df_tag <- abcde %>%
  mutate(logNote2 = case_when(
    Exe=="Execution" & Speed=="Speed"~ "Exec. & Speed",
    Speed=="Speed" & is.na(Exe) ~ "Speed",
    Exe=="Execution" & is.na(Speed)  ~ "Execution",
    .default = NA)  )%>%
  filter(!is.na(logNote2)) %>%
  select(-c(Exe,Speed,Prog,fightID)) %>%
  distinct(logID,logNote2)

rm(abcde)
```

### - Log status data

```{r}
logStatus <- df_special %>%

  group_by(logID,fightID,kill) %>%
  summarise(n=n()) %>%

  ungroup() %>%

  pivot_wider(names_from = kill,values_from = n) %>%
  group_by(logID) %>%
  summarise(`1`=sum(`1`,na.rm=T),
            `0`=sum(`0`,na.rm = T)) %>%

  ungroup() %>%

  mutate(logStatus = ifelse(`0`==0,"One-shot","Log w/ wipe(s)"))
```

### - df_final

```{r}

## Remove duplicated events - The random and topranking samples were filtered independently, but when merged had some repetitions. (i.e. they were in the random sample and in the top ranking sample)
df_special <- df_special[!(duplicated(df_special[, -which(names(df_special) == "logNote")]) | duplicated(df_special[, -which(names(df_special) == "logNote")], fromLast = TRUE)) | df_special$logNote == "Top Logs", ]



df_special_v2 <- df_special  %>%

  filter(type =="cast") %>%

  mutate(
    special = case_when(
      abilityGameID==65874 ~ "SoD",
      abilityGameID==66058 ~ "DV",
      abilityGameID==65858 ~ "SoL",
      abilityGameID==66046 ~ "LV",
      .default = NA),
    timestamp_s = (timestamp-startTime)/1000,

    f_special = factor(special,
                       labels=c("SoD","DV","SoL","LV"), levels=c("SoD","DV","SoL","LV")),

    f_kill = ifelse(kill==1,"Kill","Wipe"),
    f_diff = ifelse(difficulty==3,"Normal","Heroic"),
    logNote = ifelse(logNote=="Top Logs","Top Ranked Logs",logNote)
  ) %>%

 # filter(timestamp_s >=35 & timestamp_s<=235) %>%

  group_by(logID,fightID) %>%
  mutate(Cast_Seq = row_number()) %>%
  ungroup()  %>%


  left_join(df_tag,by=c("logID")) %>%
  mutate(logNote3 = ifelse(!is.na(logNote2),logNote2,logNote)) %>%
  filter(logNote3 != "Top Ranked Logs") %>%
  mutate(f_logNote3 =  factor(logNote3,
                              labels=c("Random Logs","Execution","Speed","Exec. & Speed"),
                              levels=c("Random Logs","Execution","Speed","Exec. & Speed"))) %>%


  filter(f_diff=="Heroic" & size==25) %>%


  left_join(logStatus,by=c("logID")) %>%
  mutate(logStatus =  factor(logStatus,
                              labels=c("One-shot","Log w/ wipe(s)"),
                              levels=c("One-shot","Log w/ wipe(s)")))

```

## Plotting

```{r}
source(file = "./scripts/2_0_plot_setting.R")
library(ggpubr)
library(ggExtra)
library("ggplotify")

```


```{r}
scale_factor = 2.65

# ` variable name `     |n      or | or
#"forge-"    
#e901 github
#e900 discord
font_add(family = "forgefooter", "forgefooter.ttf")
font_import()
showtext_auto(TRUE)
```

### - Plots 1 to 5
```{r}
source(file = "./plots/plot1.R")
source(file = "./plots/plot2.R")
source(file = "./plots/plot3.R")
source(file = "./plots/plot4.R")
source(file = "./plots/plot5.R")

coliseum <- readJPEG("_img/icon/Coliseum 4.jpg")
```


### - Plots 6 to 12

```{r}
source(file = "./plots/plot6.R")
source(file = "./plots/plot7.R")
source(file = "./plots/plot8.R")
source(file = "./plots/plot9.R")
source(file = "./plots/plot10.R")
source(file = "./plots/plot11.R")
source(file = "./plots/plot12.R")
```

### - Regional Plotting

```{r}
source(file = "./plots/region_plot.R")
```


```{r}
source(file = "./plots/plot_A.R")
source(file = "./plots/plot_B_C.R")
source(file = "./plots/plot_D.R")
source(file = "./plots/plot_E.R")

```

```{r}
df_interm <- df_special_v2  %>% filter(Cast_Seq==1 & logNote3=="Random Logs")


  ggplot() +

  geom_histogram(data=df_interm %>% filter(special=="SoD"),aes(x=hitPoints),fill="#333333",alpha=0.5) +
    geom_histogram(data=df_interm %>% filter(special=="DV"),aes(x=hitPoints),fill="#000000",alpha=0.5) +
    geom_histogram(data=df_interm %>% filter(special=="SoL"),aes(x=hitPoints),fill="#FFF0C1",alpha=0.5) +
    geom_histogram(data=df_interm %>% filter(special=="LV"),aes(x=hitPoints),fill = "#FFEB99",alpha=0.5) +

  #scale_fill_manual(values=c("#333333","#000000","#FFF0C1","#FFEB99")) +
  scale_y_continuous(labels=function(x) format(x, big.mark = ",", scientific = FALSE))

```

##### *Blank
```{r} 
###
title <- ggplot()  +
  vivax_theme_title() + 
  labs(title="",
       subtitle="") +                                                   # Remove grid, color & borders
  theme(axis.line = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())



ggsave("./_img/plot_title_white.png",title, 
       width = 4, height =4,units="in",device = "png",dpi=300)



plot_title_white  <- magick::image_read("./_img/plot_title_white.png")
```

## Canvas 1

```{r}
plot_A <- magick::image_read("./_img/plot_A.png")
plot_B <- magick::image_read("./_img/plot_D.png")
plot_C <- magick::image_read("./_img/plot_B.png")
plot_D <- magick::image_read("./_img/plot_C.png")
plot_E <- magick::image_read("./_img/plot_zoom.png")

canvas <- image_blank(width = 2900, height = 2340)

canvas <- image_composite(canvas, plot_B, offset = "+2200+0",operator = "over")

canvas <- image_composite(canvas, plot_C, offset = "+1450+50",operator = "over")
canvas <- image_composite(canvas, plot_D, offset = "+1450+750",operator = "over")

canvas <- image_composite(canvas, plot_A, offset = "+0+0",operator = "over")
canvas <- image_composite(canvas, plot_E, offset = "+0+1500",operator = "over")



image_write(canvas,paste0("./_img/twins_final4_",format(Sys.time(), "%Y_%m_%d_h%H_m%M"),".png"))
```

## Canvas 2

```{r}
plot_A <- magick::image_read("./_img/plot_A.png")
plot_B <- magick::image_read("./_img/plot_D.png")

plot_C <- magick::image_read("./_img/plot_B.png")
plot_D <- magick::image_read("./_img/plot_C.png")

canvas <- image_blank(width = 3000, height = 1500)


canvas <- image_composite(canvas,plot_C , offset = "+1450+0",operator = "over")
canvas <- image_composite(canvas, plot_B, offset = "+1450+680",operator = "over")

canvas <- image_composite(canvas, plot_A, offset = "+0+0",operator = "over")

canvas <- image_composite(canvas, plot_D, offset = "+2275+680",operator = "over")


image_write(canvas,paste0("./_img/twins_final5_",format(Sys.time(), "%Y_%m_%d_h%H_m%M"),".png"))

```

## Canvas Final

```{r}
plot_A <- magick::image_read("./_img/plot_A.png")
plot_B <- magick::image_read("./_img/plot_D.png")
plot_C <- magick::image_read("./_img/plot_B.png")
plot_D <- magick::image_read("./_img/plot_C.png")

canvas <- image_blank(width = 2900, height = 1500)

canvas <- image_composite(canvas, plot_title_white, offset = "+1450+0",operator = "over")

canvas <- image_composite(canvas, plot_B, offset = "+2200+0",operator = "over")

canvas <- image_composite(canvas, plot_C, offset = "+1450+50",operator = "over")
canvas <- image_composite(canvas, plot_D, offset = "+1450+750",operator = "over")

canvas <- image_composite(canvas, plot_A, offset = "+0+0",operator = "over")



image_write(canvas,paste0("./_img/twins_final4_",format(Sys.time(), "%Y_%m_%d_h%H_m%M"),".png"))
```

### - Extra plotting

```{r}

plot_test <- df_special_v2  %>% filter(Cast_Seq<=2 & logNote3=="Random Logs" & duration_s>=95) %>%

  left_join(df_essence,by=c("logID"="log_id",
                            "fightID"="fight_id")) %>%

  filter(!is.na(Raid_Color) & Raid_Color != "NA" & Raid_Color !="Uncertain") %>% #group_by(special) %>% summarise(n=n())%>%

  select(logID,fightID,kill,f_special,Cast_Seq) %>%

  pivot_wider(names_from = Cast_Seq,
              values_from = f_special) %>% clean_names() %>%

  filter(!is.na(x2)) %>%

  mutate(`Ability Sequence`=paste0(x1,"-",x2)) %>%

  mutate(`Ability Sequence`=factor(`Ability Sequence`,
                                   levels=c(  "SoD-DV","SoD-LV","SoD-SoL",
                                              "DV-SoD","DV-SoL","DV-LV",
                                              "SoL-DV","SoL-LV","SoL-SoD",
                                              "LV-SoL","LV-SoD","LV-DV")),
         x1 = factor(x1,
                       labels=c("SoD","DV","SoL","LV"), levels=c("SoD","DV","SoL","LV")),
         x2 = factor(x2,
                            labels=c("SoD","DV","SoL","LV"), levels=c("SoD","DV","SoL","LV"))) %>%




  ggplot() +

  geom_bar(aes(x=x2,fill=x2)) +

  scale_fill_manual(values=c("#333333",
                             "#000000",
                             "#FFF0C1",
                             "#FFEB99")) +
  scale_y_continuous(labels=function(x) format(x, big.mark = ",", scientific = FALSE))+
  vivax_theme()+
  theme(axis.text.x = element_markdown(size= scale_factor * 6,
                                       angle=0,hjust=0.5,vjust=0.6,
                                       margin = margin(t = 0,l=0, unit = "pt"),lineheight = 0),
        plot.caption = element_markdown(face = "italic",
                                        hjust = 0,
                                        vjust=0,
                                        size = scale_factor * 8,
                                        lineheight=0.3,
                                        margin = margin(t = 5,
                                                        l=0,
                                                        unit = "pt")),
        plot.title = element_markdown(face = "bold",
                                      size = scale_factor * 16,
                                      hjust = 0,
                                      margin = margin(b = 2)),
        plot.subtitle = element_markdown(lineheight = 0.35),
        axis.text = element_markdown(size= scale_factor * 6),
        axis.title.x  = element_markdown(margin = margin(b = -10))
  ) +
  guides(size="none",alpha="none",fill="none",color="none")+
  labs(y="", x="",

       title="", subtitle="") +
 #geom_vline(xintercept=c(3.5,6.5,9.5),linetype="dashed") +
  facet_wrap(.~x1,nrow=1)#,

#   caption=c("<p><span style='font-family:forgefooter'>&#xe900;</span> &emsp; discord.gg/wp55kqmyYG - Discfordge &#91;Vivax-Pagle(US)&#93; <br> <span style='font-family:forgefooter'>&#xe901;</span> https:&#47;&#47;www&#46;github.com/ForgeGit/TwinValks</p>")) #+                                                           # Remove axis labels & ticks



ggsave(paste0("./_img/plot_test_25.png"),plot_test,
       width = 10, height =2,units="in",device = "png",dpi=300)

plot_test




g <- ggplot_gtable(ggplot_build(plot_test))
strip_both <- which(grepl('strip-', g$layout$name))
fills <- c("#333333",
           "#000000",
           "#FFF0C1",
           "#FFEB99")
text_colors <- c("white", "white", "black", "black")
k <- 1
for (i in strip_both) {
  # Identify the rectangle representing the fill color
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))

  # Modify fill color
  g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]

  # Modify text color using theme
  g$grobs[[i]]$grobs[[1]]$children[[2]]$children[[1]]$gp$col <- text_colors[k]

  k <- k + 1
}

# Draw the modified plot
 grid.draw(g)


a<- as.ggplot(g)

ggsave(paste0("./_img/plot_test_25.png"),a,
       width = 10.2, height =2.8,units="in",device = "png",dpi=300)



```


```{r}
tag <- data.frame(
  logID = "https://github.com/ForgeGit/TwinValks",
  f_special = "https://discord.gg/wp55kqmyYG",
  f_logNote3 = "Vivax - Pagle (US)"
)


df_special_v2  %>%

  left_join(df_essence,by=c("logID"="log_id",
                            "fightID"="fight_id")) %>%
  
  select(logID, fightID,duration_s,f_kill,f_logNote3,logStatus,averageItemLevel,Raid_Color,
         f_special,Cast_Seq,
         timestamp_s,
         hitPoints,x,y,
         Dark_absorbs_count = Dark ,Light_absorbs_count = Light
         ) %>% 
  bind_rows(tag)%>%
  write.csv("./Twins_ability_data.csv",row.names = F)

write.csv
```




```{r}
df_master<- df_cope_spriest_master
df_interim <- df_cope_spriest_buffs_interm

class_wow <- "spriest"
class_wow_color <- "#7F1B0E"

```




#### -Canvas


##### *Title 

```{r} 
###
title <- ggplot() +
  vivax_theme_title() + 
  labs(title="<p> Trial of the Crusader (ToC) 25-man Raid<br>Stats for <b><span style='color:#7F1B0E;'>Shadow Priests</span></b> rankings - <b><span style='color:#E0C97D;'>Top 100</span></b> and <b><span style='color:#E268A8;'>Top 300</span></b></p>",
       subtitle="<p>  </p>") +                                                   # Remove grid, color & borders
  theme(axis.line = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_markdown(face = "bold",
                                      size = scale_factor * 18,
                                      hjust = 0, 
                                      margin = margin(b = -1)))

ggsave("./_img/transition/plot_title.png",title, 
       width = 10, height =4,units="in",device = "png",dpi=300)

plot_title  <- magick::image_read("./_img/transition/plot_title.png")
```

##### *Subtitle 

```{r} 
title <- ggplot()  +
  vivax_theme_title() + 
  labs(title="",
       subtitle="<p>Data from publicly uploaded logs to Warcraft Logs Classic from Aug 29 2023 21:00 to Sep 01 2023 21:00<br> <b><span style='color:#464646;'>Lower Spire</span>, <span style='color:#397000;'>Plague</span>, <span style='color:#6D0027;'>Blood</span></b> and <b><span style='color:#040A54;'>Frost</span></b> wing bosses + <b>The Frozen Throne (Lich King)</b></p>") +                                                   # Remove grid, color & borders
  theme(axis.line = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

ggsave("./_img/transition/plot_subtitle.png",title, 
       width = 12, height =4,units="in",device = "png",dpi=300)

plot_title_2  <- magick::image_read("./_img/transition/plot_subtitle.png")
```
